### 2024-05-15 README.Rmd
Even endless
Burns for you like the moon and the sun
add GH actions R CMD Check + code coverage

![GitHub License](https://img.shields.io/github/license/geryan/traveltime)
[![Lifecycle:](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
![GitHub commit activity](https://img.shields.io/github/commit-activity/w/geryan/traveltime)
![GitHub Downloads (all assets, all releases)](https://img.shields.io/github/downloads/geryan/traveltime/total)
![GitHub last commit](https://img.shields.io/github/last-commit/geryan/traveltime)
![GitHub commits since latest release](https://img.shields.io/github/commits-since/geryan/traveltime/latest)

@@

``` r
# install.packages("remotes")
remotes::install_github("geryan/traveltime")
```

@@

Here it is:
```{r}
library(sdmtools)
sin <- sdmtools::make_africa_mask(
  type = "vector",
  countries = "SGP"
)
plot(sin)
```
Get the extent of that `SpatVector` in the format we need it.
```{r}
sin_ext <- ext_from_spatraster(sin)
sin_ext
```

>>>>

<!-- badges: start -->
[![R-CMD-check](https://github.com/idem-lab/traveltime/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/idem-lab/traveltime/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/idem-lab/traveltime/branch/main/graph/badge.svg)](https://app.codecov.io/gh/idem-lab/traveltime?branch=main)
![GitHub License](https://img.shields.io/github/license/geryan/traveltime)
[![Lifecycle:](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
![GitHub commit activity](https://img.shields.io/github/commit-activity/w/geryan/traveltime)
![GitHub Downloads (all assets, all releases)](https://img.shields.io/github/downloads/geryan/traveltime/total)
![GitHub last commit](https://img.shields.io/github/last-commit/geryan/traveltime)
![GitHub commits since latest release](https://img.shields.io/github/commits-since/geryan/traveltime/latest)
<!-- badges: end -->

@@

``` r
# install.packages("remotes")
remotes::install_github("idem-lab/traveltime")
```

@@

Here it is:
```{r}
library(sdmtools)
sin <- sdmtools::make_africa_mask(
  type = "vector",
  countries = "SGP"
)
plot(sin)
```
Get the extent of that `SpatVector` in the format we need it.
```{r}
sin_ext <- ext_from_terra(sin)
sin_ext
```
